Reviewer comments from PeerJ

### 2015-03-24 PeerJResponse.tex
edits to response

\res{We have conducted our NJ analysis with 1000 rather than 100 bootstraps and results are qualitatively very similar.}

>>>>

\res{We actually conducted our NJ analysis with 10,000 bootstrap replicates and mistakenly reported 100 replicates.  This is clear based on our bootstrap support values which are reported to two decimal places.  We have corrected this typo.}
